The regularity of ODEs and thimble integrals \\ with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}

### 2024-11-14 borel-regularity.tex
Remove cantilever thimble integral drafts

If we had a thimble integral expression for $V_\alpha$, we could use the thimble projection formula, as written in equation~\eqref{eqn:formula-proof}, to find $v_\text{uni}$. Since we found $v_\text{uni}$ in Section~\ref{sec:solve-cantilever-eqn}, we can work backwards from equation~\eqref{thimble-difference} to guess a thimble integral expression for $V_\alpha$.
We hope to express $V_\alpha$ in the form

@@

where $f$ is a holomorphic function on $\C$, $u$ is the standard coordinate on $\C$, $a$ is a critical point of $f$ with $f(a) = \alpha$, and $\mathcal{C}_a^\theta$ is the component of $f^{-1}\big(\alpha + e^{i\theta}[0, \infty)\big)$ that runs through $a$. We know from equation~\eqref{thimble-difference} that this thimble integral will evaluate to $V_\alpha$ as long as

@@

From our formula for $f$ in terms of $\operatorname{sd}$, we can see that $f$ is odd at $a$ with respect to $u$, implying that
\[ \left.\frac{du}{df}\right|_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)} = -\left.\frac{du}{df}\right|_{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}\,. \]
We can therefore rewrite equation~\eqref{eqn:cantilever-endpoint} as
\[ \frac{1}{\sqrt{\zeta^4-\omega^2}} = \left[\frac{du}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}\,, \]
confirming that our guess for $f$ satisfies equation~\eqref{eqn:cantilever-thimble-difference}. It follows that
\[ V_\alpha = \int_{\mathcal{C}_a^\theta} \exp\left[ -z\,2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big) \right]\;du. \]

%%Knowing that the inverse of $\operatorname{sn}$ is the incomplete elliptic integral
%%\begin{equation}
%%F(x;k):=\int_0^x \frac{dt}{\sqrt{(1-t^2)(1-k^2t^2)}}\,,
%%\end{equation}
\end{revised}

\begin{draft}
Equation~\eqref{eqn:formula-proof} becomes
\[ \frac{1}{\sqrt{\zeta^4-\omega^2}} = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\,du \right). \]
\[ \frac{d\zeta}{\sqrt{\zeta^4-\omega^2}} = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\,du \right)d\zeta. \]
\[ \frac{d\zeta}{\sqrt{\zeta^4-\omega^2}} = d\Big[ \left( \int_{\mathcal{C}_a^\theta(\zeta)}\,du \right)\Big]. \]
If we guess that $\operatorname{start} \mathcal{C}_a^\theta(\zeta) = -\operatorname{end} \mathcal{C}_a^\theta(\zeta)$, we can rewrite the equation above as
\[ \frac{1}{2}\left[\frac{d\zeta}{\sqrt{\zeta^4 - \omega^2}}\right] = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\,du \right). \]
\end{draft}

\begin{draft}
We assume that $V_\alpha$ has the following expression 
\[\int_{\mathcal{C}_a^\theta}e^{-z f} du\]
for unknown function $f$, and $\mathcal{C}_a^\theta:=f^{-1}\big((\alpha,e^{i\theta}\infty)\big)$ with $f(a)=\alpha$. Then, for $\zeta=f$ equation~\eqref{thimble-difference} becomes
\[ \frac{1}{\sqrt{\zeta^4-\omega^2}} = \left[\frac{du}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}. \]
Let us guess that $f$ maps the real $u$ axis into the real $\zeta$ axis, so $f$ is equivariant with respect to conjugation and the path $\mathcal{C}_a^\theta$ is symmetric with respect to conjugation. Then we can rewrite the equation above as
\begin{align*}
\frac{1}{2} \left[ \frac{1}{\sqrt{\zeta^4 - \omega^2}} \right] & = \left.\frac{du}{df}\right|_{\operatorname{end} \mathcal{C}_a^\theta(\zeta)} \\
\frac{1}{2} \left[ \frac{df}{\sqrt{\zeta^4 - \omega^2}} \right] & = du \\
\frac{1}{2} \left[ \frac{f^* d\zeta}{\sqrt{\zeta^4 - \omega^2}} \right] & = du
\end{align*}
\begin{align*}
\frac{1}{2} \left[ \frac{1}{\sqrt{\zeta^4 - \omega^2}} \right] & = \frac{du}{df} \\
\frac{1}{2i \omega \sqrt{1 - \omega^{-2} \zeta^4}} & = \frac{du}{df} \\
\frac{\omega^{-1/2}}{\sqrt{1 - (\omega^{-1/2} \zeta)^4}} & = 2i \omega^{1/2}\;\frac{du}{df} \\
F(\omega^{-1/2} \zeta; i) & = 2i \omega^{1/2} u\,,
\end{align*}
where the function $F$ is the inverse of the elliptic sin function $\operatorname{sn}$
\begin{equation}
F(x;k):=\int_0^x \frac{dt}{\sqrt{(1-t^2)(1-k^2t^2)}}\,.
\end{equation}
\end{draft}
%Suppose $V_\alpha$ can be expressed as a thimble integral.

\begin{todo}[The narrative here doesn't seem to make sense. Rewrite]\end{todo} \begin{old}We can now use the thimble projection formula, as written in equation~\eqref{thimble-difference}, to express the solutions found above as thimble integrals. In terms of the Jacobi elliptic function $\operatorname{sd}$, we have
\begin{equation}\label{eq:cantilever-thimble}
V_\alpha = \int_{\mathcal{C}_a^\theta} \exp\left[ -z\,2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big) \right]\;du,  \end{equation}
where $a$ is a preimage of $\zeta = \alpha$ under the map $\zeta = 2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big)$. \begin{todo}[\textbf{A} Show thimble picture.]\end{todo} Since exponent is doubly periodic, with period lattice $L = \tfrac{1}{\sqrt{2}}\Z + i\Z$, we can take the thimble to be a real submanifold of the torus $\C / L$.

To confirm equation~\eqref{eq:cantilever-thimble}, use Jacobi's transformations to rewrite the relationship between $\zeta$ and $u$ in terms of $\operatorname{sn}$.
\[ \zeta = \omega^{1/2} \operatorname{sn}\big(2i \omega^{1/2} u, i\big). \]
Jacobi's imaginary transform gives
-i \operatorname{sn}\big(2i \omega^{1/2} u, \sqrt{1-\sqrt{2}^2}\big) & = \operatorname{sc}(2\omega^{1/2} u, \sqrt{2}) \\
\operatorname{sn}\big(2i \omega^{1/2} u, i\big) & = i \operatorname{sc}\big(2\omega^{1/2} u,\sqrt{2}\big)
Jacobi's real transform gives
\frac{1}{2\omega^{1/2}} \operatorname{sc}\big(2\omega^{1/2} u, \tfrac{1}{1/\sqrt{2}}\big) & = \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big) \\
i \operatorname{sc}\big(2\omega^{1/2} u, \tfrac{1}{1/\sqrt{2}}\big) & = 2i \omega^{1/2} \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big).
Altogether, we have
\operatorname{sn}\big(2i \omega^{1/2} u, i\big) & = 2i \omega^{1/2} \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big) \\
\omega^{1/2} \operatorname{sn}\big(2i \omega^{1/2} u, i\big) & = 2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big)
Knowing that the inverse of $\operatorname{sn}$ is the incomplete elliptic integral
F(x;k):=\int_0^x \frac{dt}{\sqrt{(1-t^2)(1-k^2t^2)}}\,,
F(\omega^{-1/2} \zeta; i) & = 2i \omega^{1/2} u \\
\frac{\omega^{-1/2}\;d\zeta}{\sqrt{1 - (\omega^{-1/2} \zeta)^4}} & = 2i \omega^{1/2}\;du \\
\frac{d\zeta}{2i \omega \sqrt{1 - \omega^{-2} \zeta^4}} & = du \\
\frac{1}{2}\left[\frac{d\zeta}{\sqrt{\zeta^4 - \omega^2}}\right] & = du.
\end{old}
\begin{todo}[Note that this presents $V_\alpha$ as the Laplace transform of $v_\text{uni}$.]\end{todo} \begin{todo}[Explain how symmetry of thimble gives $v_\text{uni}$ under thimble projection formula.]\end{todo}
%\subsection{The anharmonic oscillator}\label{sec:anharmonic_oscillator}

>>>>

If we had a thimble integral expression for $V_\alpha$, we could use the thimble projection formula, as written in equation~\eqref{eqn:formula-proof}, to find $v_\text{uni}$. Since we found $v_\text{uni}$ in Section~\ref{sec:solve-cantilever-eqn}, we can work backwards from equation~\eqref{thimble-difference} to guess a thimble integral expression for $V_\alpha$. We hope to express $V_\alpha$ in the form

@@

where the function $f$ is a holomorphic function on $\C$, the function $u$ is the standard coordinate on $\C$, the point $a$ is a critical point of $f$ with $f(a) = \alpha$, and the path $\mathcal{C}_a^\theta$ is the component of $f^{-1}\big(\alpha + e^{i\theta}[0, \infty)\big)$ that runs through $a$. We know from equation~\eqref{thimble-difference} that this thimble integral will evaluate to $V_\alpha$ as long as

@@

From our formula for $f$ in terms of $\operatorname{sd}$, we can see that $f$ is odd at $a$ with respect to $u$, implying that
\[ \left.\frac{du}{df}\right|_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)} = -\left.\frac{du}{df}\right|_{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}\,. \]
We can therefore rewrite equation~\eqref{eqn:cantilever-endpoint} as
\[ \frac{1}{\sqrt{\zeta^4-\omega^2}} = \left[\frac{du}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}\,, \]
confirming that our guess for $f$ satisfies equation~\eqref{eqn:cantilever-thimble-difference}. It follows that
\[ V_\alpha = \int_{\mathcal{C}_a^\theta} \exp\left[ -z\,2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big) \right]\;du\,. \]
Since the exponent is doubly periodic, with period lattice $L = \tfrac{1}{\sqrt{2}}\Z + i\Z$, we can take the thimble to be a real submanifold of the torus $\C / L$.
